Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-21 referee.tex
Revising points C and D

We apologize for not being more clear on this point.  \textbf{As seen in Figure \ref{fig:compare_mass}, there are seven stars that form in a halo with $M_{\rm halo} > 10^8 M_\odot$ but are actually hosted by a subhalo that hasn't been enriched yet. \textit{DS -- this figure was removed for simplicity}} This is an interesting case within itself.  We might follow up on this object in a later study because it's outside the scope of the paper.  Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.  Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.  We have added some clarifying text to the first paragraph of the Section 3.1.

@@

1\% of Pop III stars form in a halo not identified by Rockstar. This has been added to the Population III Host Halo Masses subsection. To be clear, Pop III stars should not be forming outside of halos. This small percentage of Pop III stars are forming in halos, but in halos not identified by Rockstar.

Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line.

The baryon fraction varies with time at the lowest mass scales, just above the cosmological jeans mass, around $10^{4} M_{\odot}$. In our work, we are looking at halos above that value by about a factor of 20. At this point, the halos have had time to collect baryons. In general, the baryon fraction is dependent on redshift in our work due to feedback, not cosmological effects. This results in a range of average baryon fractions for halo masses throughout our simulation. In Figure \ref{fig:avg_baryon_fraction}, the halos with smaller masses tend to have low average baryon fractions due to resolution effects and feedback.

>>>>

We apologize for not being more clear on this point.  There are seven stars that form in an atomic cooling halo but are actually hosted by a subhalo that hasn't been enriched yet. This is an interesting case within itself.  We might follow up on this object in a later study because it's outside the scope of the paper.  Because we take the parent halo mass as the host halo mass, we did not include these stars in the analysis because the parent halo mass is not representative of the cooling processes inside of the subhalo.  Because this is a rare event in our simulation (7 out of 688 Pop III stars), it does not shift the average halo mass by a significant amount.  We have added some clarifying text to the first paragraph of the Section 3.1.

@@

There are 1\% of Pop III stars that form in a halo not identified by Rockstar.  To be clear, Pop III stars should not be forming outside of halos. This small percentage of Pop III stars are forming in halos but in halos not identified by Rockstar.  We have added these details to the ``Population III Host Halo Masses" subsection.

\jhw{Need to double-check baryon fraction figure.}

Figure \ref{fig:avg_baryon_fraction} shows the average baryon fraction for each halo as a function of the halo mass. The cosmic baryon fraction is shown as a solid black line. The baryon fraction only should smoothly increase with time as it grows from the cosmological Jeans mass, around $10^{4} M_{\odot}$.  Our simulations do not resolve this mass scale, but the baryon fraction will be slightly lower than the cosmic value ($\Omega_b/\Omega_m$) in the smallest resolved halos ($2 \times 10^5 M_\odot$ are sampled with 100 particles).  However above this mass scale, the baryon fraction will greatly vary with time due to feedback, not cosmological effects. This results in a range of average baryon fractions for halo masses throughout our simulation. In Figure \ref{fig:avg_baryon_fraction}, the halos with smaller masses tend to have low average baryon fractions due to resolution at the very low-mass end and feedback once they have hosted star formation.
